Model of lens candidates from Space Warps CFHTLS

### 2016-07-08 paper2.tex
editing

@@

Section~\ref{sec:spl}

@@

\section{Stellar mass}

@@

\section{Summary of models}

>>>>

\newcommand{\Mstel}{M_{\rm stel}}
\newcommand{\Mhalo}{M_{\rm h}}
\newcommand{\haloindex}{\mathcal{H}}

@@

Section~\ref{sec:spl} explains the SpaghettiLens system.

Section~\ref{sec:stellar-mass} is about stellar mass.

Section~\ref{sec:examples} discusses ten systems in detail.

Section~\ref{sec:summary} has a summary table.

@@

\section{Stellar mass}\label{sec:stellar-mass}

Based on \cite{2003MNRAS.344.1000B} models.

Following \cite{2010ApJ...710..903M}
\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
                                     (\Mhalo/M_1)^\gamma} \\
C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}

\begin{equation}
\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
which we may call the halo-matching index.
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
  lensing mass.
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance-matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}

@@

\section{Summary of models}\label{sec:summary}
